Hydras \& Co.

### 2023-02-16 doc/hydras.tex
documentation on FOL (draft)
fix an inconsistent section numbering

\part{Ackermann, G\"{o}del, Peano\,\dots}
This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

@@

>>>>

\part{Ackermann, G\"{o}del, Peano\,\dots}

This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

@@

\begin{todo}
Add information on recent developments on formal 
proofs of G\"odel  incompleteness theorems. Justify the decision of working on \emph{this} development.  
\end{todo}
